Deep Learning

### 2015-01-12 deepreview.tex
moved Geoff's refs from aigaion.bib to ml.bib and added a GSN citation

This review has focused on supervised learning because of its recent
achievements and we have ignored much interesting work on unsupervised
learning procedures for deep neural 
networks~\citep{Salakhutdinov2009-small,Hinton95,QuocLe-ICML2012,VincentPLarochelleH2008-small,ranzato-pami,Kingma-et-al-NIPS2014}. 
In the long run,
however, we believe unsupervised learning will be essential for allowing
deep networks to generalize well by creating internal representations that
untangle the many different factors that interact to produce images, speech
and documents~\citep{Bengio-Courville-Vincent-TPAMI2013}.

>>>>

This review has focused on supervised learning because of its recent
achievements and we have ignored much interesting work on unsupervised
learning procedures for deep neural 
networks~\citep{Salakhutdinov2009-small,Hinton95,QuocLe-ICML2012,VincentPLarochelleH2008-small,ranzato-pami,Bengio-et-al-ICML-2014,Kingma-et-al-NIPS2014}. 
In the long run,
however, we believe unsupervised learning will be essential for allowing
deep networks to generalize well by creating internal representations that
untangle the many different factors that interact to produce images, speech
and documents~\citep{Bengio-Courville-Vincent-TPAMI2013}.
